PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added OCI-R sum score differences chunk. Needs to be tested once data is ready (awaiting IDs to be fixed).

>>>>

OCI-R difference scores
```{r ocir difference scores}
# Difference score for prepandemic and retrospective oci-r sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_prepan_retro =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$ocir.diff_score_prepan_retro)

# Difference score for prepandemic and baseline ocir sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_prepan_base =
      as.numeric(
        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

summary(dat.glad$ocir.diff_score_prepan_base)

# Difference score for retrospective and baseline ocir sum scores
dat.glad <- dat.glad %>%
  mutate(
    ocir.diff_score_base_retro =
      as.numeric(
        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$ocir.diff_score_base_retro)
